Supplemental Material for ``Assessing United States county-level exposure for research on tropical cyclones and human health"

### 2019-07-27 writing/anderson_ehp_supp.tex
Work on draft throughout

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.7\linewidth]{hurrtracks}
\caption{Tracks of all tropical cyclones included in the study. The study
included all tracked storms in the revised Atlantic hurricane database
\ac{HURDAT2}~\citep{landsea2013} that came within 250~\si{\kilo\metre} of at least on
\ac{US} county, 1988\,--\,2015. Thicker lines show the tracks of storms whose
names were retired, indicating that the storm was particularly severe or had
notable impacts~\citep{retirednames}.}
\label{fig:hurrtracks}
\end{figure}

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=\linewidth]{averageexposureonlysupp}
\caption{Average number of storm exposure per decade in \ac{US} counties for
each exposure metric, based on years of for which data for all five exposure
metrics are available (1996\,--\,2011). The criteria behind each of the five
metrics is given in Table 1 of the main text.} \label{fig:averageexposuresupp}
\end{figure}

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=\linewidth]{windexamples}
\caption{Wind classifications for the two storms, Hurricanes Sandy (2012) and
Ike (2008) for which exposure classifications from modeled wind
data~\citep{stormwindmodel} and \ac{HURDAT2} wind
radii~\citep{demuth2006improvement} showed the highest disagreement for storms
between 2004 and 2015 (Figure~\ref{fig:windcomparison}). The top two maps show
modeled (left) and \ac{HURDAT2} (right) windspeed categorizations for Hurricane
Ike (2008), while the bottom two maps show the same windspeed characterizations
for Hurricane Sandy (2012).  In both cases, the storms were exceptionally large
systems for which high winds persisted well inland from landfall and for which,
based on the \ac{HURDAT2} data, a large number of counties were exposed to
winds of $\ge$34 knots (Figure~\ref{fig:windcomparison}).}
\label{fig:windexamples}
\end{figure}

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.9\linewidth]{rainexamples}
\caption{Examples of storms where the rain exposure classification method fails
to capture full storm-related rainfall because of the distance constraint used
in that assessment metric. The red line on each map shows the track of the
storm, based on the revised Atlantic hurricane database
\ac{HURDAT2}~\citep{landsea2013}. The color of each county in the map gives the
cumulative precipitation (in millimeters) for that county during the window
from two days before to one day after the storm's closest approach to the
county. The blue outline identifies the collection of counties that were
classified as ``exposed" based on the criteria that the storm passed within
500~\si{\kilo\metre} of the county's population mean center and the cumulative
rainfall was 75 millimeters or more (Table 1 of main text). The map on the left
shows rain-based exposure for Hurricane Ike. For this exceptionally large
storm, there are some counties in northern Texas that received high rainfall
from the storm but are too far from the storm center's track to be classified
as exposed by this metric. The map on the right shows rain-based exposure for
Tropical Storm Lee. For this storm, rain from the storm affected counties in
the Mid-Atlantic and New England as the remnants of the storm moved over those
regions, but storm tracking stopped while the storm was still over the
southeastern part of the \ac{US}, and so these counties are not classified as
exposed to the storm based on this metric.}
\label{fig:rainexamples}
\end{figure}

@@

\bibliography{hurr_exposure}

>>>>

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=\linewidth]{averageexposureonlysupp}
\caption{Average number of storm exposure per decade in \ac{US} counties for
each exposure metric, based on years of for which data for all five exposure
metrics are available (1996\,--\,2011).} 
\label{fig:averageexposuresupp}
\end{figure}

@@

\begin{figure}[tbhp!]
\centering
\includegraphics[width=\linewidth]{windexamples}
\caption{Comparison of county-level estimates of maximum sustained surface wind speeds
	for Hurricane Ike in 2008 (top) and Hurriance Sandy in 2012 (bottom). 
	Each map shows the estimated maximum sustained surface wind speed 
	classification ($<$34~\si{\knot}; 34\,--\,49.9~\si{\knot}; 
	50\,--\,63.9~\si{\knot}; $\ge$64~\si{\knot}) for each study county. 
	The maps labelled ``Modeled'' (left)
	shows the classifications based on modeled sustained surface wind
	speeds, which were included in the open-source data as the main 
	wind metric and used in further analysis in this research. The maps
	labelled ``Extended Best Tracks'' (right) show classifications based on the 
	wind radii given in \ac{HURDAT2} (included as a secondary wind 
	metric in the open-source data). The red lines show the storms' 
	tracks.
	}
\label{fig:windexamples}
\end{figure}

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.9\linewidth]{rainexamples}
\caption{Examples of storms where the rain exposure classification method fails
to capture full storm-related rainfall because of the distance constraint used
in that assessment metric. The red line on each map shows the track of the
storm. The color of each county in the map gives the cumulative precipitation
(in \si{\milli\metre}). The blue outline identifies the collection of counties
that were classified as ``exposed" based on our rainfall criteria (Table 1 of
main text). }
\label{fig:rainexamples}
\end{figure}

@@

\printbibliography

### 2019-07-27 writing/ehp_discussion.tex
Work on draft throughout

Tropical cyclones impact public health in many ways, and epidemiological
studies of the health risk and impacts associated with tropical cyclone
exposures could help improve preparedness for and response to future tropical
cyclones.  However, tropical cyclones are multi-hazard events, making it more
complicated to measure exposure compared to other weather exposures like
temperature and precipitation. Here, we find the county-level tropical cyclone
exposure assessments vary substantially when using a distance-based metric
versus four hazard-based metrics, as well as among different hazard-based
metrics. Our results can inform exposure assessment for future county-level
studies of the health risks and impacts associated with tropical cyclones
exposures, and the data and software we have created to accompany this article
provides multi-hazard, county-level exposure data for multiple tropical cyclone
hazards for such studies.

Distance from a tropical cyclone's track is relatively easy to measure and has
been used as an operational metric of exposure to tropical cyclones in previous
large-scale studies (examples include ...). Since distance itself
does not constitute a hazard, distance is meant in these cases as a surrogate
to capture exposure to hazards from the tropical cyclone. However, here we
found that in assessing \ac{US} county-level exposure to tropical cyclones,
distance is, at best, a moderate, and often a very poor, surrogate for exposure
to the specific tropical cyclone hazards of high wind, extreme rainfall,
flooding, and tornadoes (Figure~\ref{fig:jaccard}).  Therefore, use of distance
to assess tropical cyclone exposure for impact studies could result in
problematic exposure misclassification, which could mask true associations,
even strong associations, between tropical cyclone exposure and outcomes of
interest in impact studies~\parencite{savitz2016interpreting, armstrong1998effect}.

In some cases, this exposure misclassification may be differential (i.e.,
associated with the outcome of interest or with factors associated with risk of
the outcome of interest). For example, tropical cyclone wind exposures tend to
be concentrated in counties near the coast, since most tropical cyclones
rapidly decrease in sustained windspeed following landfall. However, tropical
cyclone exposures based on distance can extend well inland, following the
tropical cyclone's tracks, but may not adequately capture all wind-exposed
counties near the coast. In this case, if the etiologically-relevant exposure
is high wind but exposure is classified based on distance, the probability of
being misclassified as unexposed would be higher in coastal counties, while the
probability of being misclassified as exposed would be higher in inland
counties. If coastal counties differ from inland counties in either the outcome
of interest or in factors associated with risk of that outcome, differential
exposure misclassification would exist~\parencite{savitz2016interpreting}. Such
differential exposure misclassification can bias estimates of tropical cyclone
effects either towards the null (estimating a lower or null association
compared to the true association that exists) or away from the null (estimating
a larger association than actually exists)~\parencite{savitz2016interpreting,
armstrong1998effect}. The use of a single hazard-based metric (e.g., wind)
could cause similar problems if the impact is driven, at least in part, by a
different hazard or by multiple hazards of the tropical cyclone.

Our findings\,---\,that county-level tropical cyclone exposure assessment varies
substantially when different exposure measurements are considered\,---\,aligns with
previous research from atmospheric science and related fields on the
characteristics of tropical cyclones. While tropical cyclone rainfall and
windspeed are often well-correlated when the tropical cyclone is over
water~\parencite{cerveny2000}, this relationship often does not remain as strong
once the hurricane has made landfall~\parencite{jiang2008}.  Fast-moving tropical
cyclones bring higher risks of dangerous winds inland~\parencite{kruk2010}, while
slow-moving tropical cyclone are likely to bring more
rain~\parencite{rappaport2000} and cause more damage because of sustained hazardous
conditions~\parencite{rezapour2014}. Further, while the likelihood and extent of
flooding during a tropical cyclone is related to the tropical cyclone's
rainfall, it is also driven by factors like top soil saturation and the
structure of the water basin's drainage network~\parencite{chen2015, rees2001}.
However, we did find a small set of tropical cyclones for which for which
agreement between metrics were unusually high (e.g., Floyd in~1999, Irene in
2011, Hannah in~2008, Bertha in~1996) For this set of tropical cyclones, the
tropical cyclones' persistent proximity to water may have helped maintain wind
speeds in similar patterns to rain and distance exposures, resulting in this
moderate to good agreement among exposure assessments based on different
metrics.

In our results, wind-based exposure had a strong coastal pattern, with almost
all exposures in counties within about~200~\si{\kilo\metre} (124~mi) of the
coastline. This is consistent with the dramatic decrease in wind intensity that
typically characterizes the landfall of tropical cyclones. Exposures by rain-
and distance-based metrics often extended further inland compared to the
wind-based metric, up to the Appalachian mountains. This agrees with previous
research indicating that the Appalachian mountains' topography both enhances
precipitation during tropical cyclones and provides hydrological conditions for
severe flooding~\parencite{rees2001}.  Almost all tornado-based exposures were in
southern coastal states. This pattern echoes previous findings that most
noteworthy tropical cyclone-related tornadoes occur on the right-side of the
tropical cyclone track in Atlantic-basin \ac{US} storms~\parencite{moore2012}.

The tropical cyclone exposure averages shown in
Figure~\ref{fig:averageexposure} are limited as estimates of long-term
frequencies, as tropical cyclones follow decadal
patterns~\parencite{kossin2007more} likely not adequately captured in the available
data.  However, these frequency maps, together with evidence from specific
tropical cyclones (Figures~\ref{fig:ivanexposure} and~\ref{fig:jaccard}),  do
illustrate the potential for strong differences in spatial patterns in tropical
cyclone exposures, depending on which tropical cyclone hazards are considered.
A few previous studies have sought to determine county-level exposure to
tropical cyclones over multi-year periods, including~\textcite{zandbergen2009},
which estimated exposure in \ac{US} counties to all \ac{US} landfalling
Atlantic-basin tropical cyclones between~1851 and~2003, using both a
distance-based metric and a metric that combined distance and windspeed,
and~\textcite{kruk2010}, which explored exposure to hurricane-related winds in the
\ac{US}, including inland areas, for~1900\,--\,2008.  Our results suggest that
such exposure assessments may perform well in capturing some tropical cyclone
hazards (e.g., wind), but likely miss other potentially dangerous tropical
cyclone exposures, especially for hazards that repeatedly threaten northern or
inland counties (e.g., rain, flooding).

Dissimilarity in exposure to specific hazards of tropical cyclones can result
in differing patterns in estimates of county-level exposure
(Figure~1\todo{change to fig. ref}), which can lead to substantial differences
in estimates of population physical exposure
(Figure~\ref{fig:topelecdependexposure}), based on which storm hazard is
considered. The measure of a hurricane's intensity, the Saffir-Simpson scale,
expresses intensity as a function of wind speed, and so fails to capture
potential risks from other hazards of the storm~\parencite{smith2009}, and
previous assessments of physical exposure to tropical cyclones have often
focused on winds or distance from the storm. For example, a global study of
exposure and vulnerability to natural hazards used a combination of windspeed
above a certain threshold and distance from the storm's track to assess
exposure~\parencite{peduzzi2009assessing}. While many storm impacts might be
most strongly linked to wind hazards, there is a growing recognition of the
potential risks of adverse health outcomes and property damage from rain- and
flood-related tropical cyclone hazards in the \ac{US}~\parencite{smith2009}.
Such assessments may underemphasize potentially dangerous exposures to certain
regions of the \ac{US}, particularly inland locations. In fact, based on our
assessment of physical exposures to tropical cyclones among
electricity-dependent Medicare beneficiaries, the highest expected physical
exposure under any metric was measured for Philadelphia County, PA, under the
flood metric (Figure~\ref{fig:topelecdependexposure}).  While this county has a
similar-sized population of electricity-dependent Medicare beneficiaries as
Miami-Dade County, FL (Figure~\ref{fig:topelecdependexposure}), the frequency
of storm-related flood events in this inland county results in a very high
expected physical exposure among this subpopulation, while this county is not
included in the top ten counties for physical exposure based on most of the
other exposure metrics.

\subsection*{Software}

To assist with future tropical cyclone studies, we created and published open
source software to accompany this article~\parencite{hurricaneexposuredata,
hurricaneexposure}. Many previous studies have used geographical
information system software (e.g., ArcGIS) to assess exposure to tropical
cyclones in the \ac{US}~\parencite{grabich2016, zandbergen2009, czajkowski2011,
kruk2010}. Here, we offer methods to map and output historic exposure to
tropical cyclones that does not require the use of proprietary software but
instead uses a package written in the R statistical programming
language~\parencite{R}, which is free and open-source.

In addition to providing tropical cyclone exposure metrics for individual
hazards, this software and data also allow users to create tropical cyclone
exposure profiles based on multiple hazards or craft exposure indices that
combine hazard metrics~\parencite{chakraborty2005population, peduzzi2009assessing}.
This ability can be critical, as different hazards of tropical cyclones
often act synergistically in causing impacts~\parencite{smith2009}. Further, by
including measurements of different hazard exposures in each county for each
tropical cyclone, this software allows for the development of more complex
exposure indices or models (e.g., random forests, multivariable generalized
linear models) that incorporate multiple tropical cyclone hazard measurements.

In creating this hurricane exposure dataset, we aimed for data that are
reliable, available for all eastern \ac{US} counties, and have no missing data
within available dates. Further, we have investigated how well these data
correspond with data from other available sources
(Figures~S7\,--\,11\todo{Check fig refs}). While generally in agreement with
data from other sources, there are a few limitations. The wind data are based
on modeled, rather than observed, values, and while the modeled wind data
generally agree well with post-analysis maximum wind radii from
\ac{HURDAT2}~\parencite{landsea2013} (Figure~S7\todo{Check fig refs}), for a
few tropical cyclones it did not (e.g., Figure~S10\todo{Check fig refs}). The
rainfall data are from re-analysis data, which are generally well-correlated
with observed ground-based station data but sometimes oversmooth extreme
measurements (Figure~S8\todo{Check fig refs}).  The flood and tornado data came
from the \ac{NOAA} Storm Events database, which, while a widely-used database
of events maintained by \ac{NOAA}, is based on reports, and so may be prone to
underreporting~\parencite{Ashley2008flood, Curran2000}, especially in less
populated areas~\parencite{Witt1998, Ashley2007}, as well as to other reporting
errors. While these are important limitations, we selected these data sources
as among the best currently available for measuring each of these hazards at a
multi-county, multi-year scale.

>>>>

Tropical cyclones impact public health in many ways, and epidemiological
studies of the health risk and impacts associated with tropical cyclone
exposures could help improve preparedness for and response to future tropical
cyclones.  However, tropical cyclones are multi-hazard events, making it
complicated to measure exposure. Here, we provide open-source county-level data
on multiple storm exposure metrics, and we find that county-level tropical
cyclone exposure assessments vary substantially when using a distance-based
metric versus four hazard-based metrics, as well as among different
hazard-based metrics. Our results can inform exposure assessment for future
county-level studies of the health risks and impacts associated with tropical
cyclones exposures, and the open-source data and software we have created
provides multi-hazard, county-level exposure data for such studies.

\subsection*{Exposure assessment data and software}

In creating this hurricane exposure dataset, we aimed for data that are
available for all eastern \ac{US} counties. In addition to providing tropical
cyclone exposure metrics for individual hazards, this data and its associated
software allow users not only to access measurements for single hazards, but
also to create tropical cyclone exposure profiles based on multiple hazards or
craft exposure indices that combine hazard
metrics~\parencite{chakraborty2005population, peduzzi2009assessing}. This
ability can be critical, as different hazards of tropical cyclones often act
synergistically in causing impacts~\parencite{smith2009}.

\begin{comment}
To assist with future tropical cyclone studies, we created and published open
source software with this dataset and accompanying
tools~\parencite{hurricaneexposuredata, hurricaneexposure}.  Many previous
studies have used geographical information system software (e.g., ArcGIS) to
assess exposure to tropical cyclones in the \ac{US}~\parencite{grabich2016,
zandbergen2009, czajkowski2011, kruk2010}.  Here, we offer methods to map and
output historic exposure to tropical cyclones that does not require the use of
proprietary software but instead uses a package written in the R statistical
programming language~\parencite{R}, which is free and open-source.  Further, by
including measurements of different hazard exposures in each county for each
tropical cyclone, this software allows for the development of more complex
exposure indices or models (e.g., random forests, multivariable generalized
linear models) that incorporate multiple tropical cyclone hazard measurements.  
\end{comment}

We investigated how well these data correspond with data from other available
sources (Figures~\ref{fig:windcomparison}\,--\,\ref{fig:floodcomparison}
and~S6\,--\,7). While generally in agreement with data from other sources,
there are a few caveats that should be considered when applying these data in
future studies. The rainfall data are from re-analysis data are generally
well-correlated with observed ground-based station data, but may sometimes
oversmooth very high rainfall values compared to ground-based observations
(Figure~\ref{fig:raincomparison}). When rainfall data is used to create binary
exposure classifications, this disagreement is unlikely to influence results,
as both data sources agree in identifying these as storms with high rainfall,
but it may be important to consider for cases that include rainfall as a
continuous measurement.

The wind data are based on modeled, rather than observed, values, and while the
modeled wind data generally agree well with post-analysis maximum wind radii
from \ac{HURDAT2}~\parencite{landsea2013} (Figure~\ref{fig:windcomparison}),
there were a few storms where the two datasets did not agree as well ($<$90\%
of counties classified into the same wind categories by the two sources of wind
estimates). These storms were exceptionally large systems for which high winds
persisted well inland from landfall, like Hurricanes Sandy and Ike
(Figures~\ref{fig:windcomparison} and\~S6). Since the wind radii are based on
\ldots, they have [advantages]; their main disadvantages is that they provide
categorical, rather than continuous, estimates of wind speed, and in many cases
researchers might prefer more precise estimates of storm wind speeds. However,
since the wind radii data may be useful in some cases as either a primary
metric or for sensitivity analysis, we have include county-level wind estimates
for each storm based on these wind radii, in addition to the continuous modeled
windspeeds, in the open-source data \cite{hurricaneexposuredata}.

The flood and tornado data came from the \ac{NOAA} Storm Events database,
which, while a widely-used database of events maintained by \ac{NOAA}, is based
on reports, and so may be prone to underreporting~\parencite{Ashley2008flood,
Curran2000}, especially in less populated areas~\parencite{Witt1998,
Ashley2007}, as well as to other reporting errors. While these are important
limitations, we selected these data sources as among the best currently
available for measuring each of these hazards at a multi-county, multi-year
scale.

\subsection*{Patterns in tropical cyclone exposures}

We found geographic patterns in tropical cyclones based on the different
exposure metrics that. These patterns were not unexpected based on what is
known about tropical cyclone hazards, but still highlight variations across
metrics that are critical to consider in designing studies for tropical cyclone
epidemiology, and they demonstrate the need for multi-hazard exposure datasets
for tropical cyclone epidemiology. Wind-based exposures had a strong coastal
pattern, which is consistent with the dramatic decrease in wind intensity that
typically characterizes the landfall of tropical cyclones. Exposures by rain-
and distance-based metrics often extended further inland compared to the
wind-based metric, up to the Appalachian mountains. This agrees with previous
research indicating that the Appalachian mountains' topography both enhances
precipitation during tropical cyclones and provides hydrological conditions for
severe flooding~\parencite{rees2001}.  Almost all tornado-based exposures were
in southern coastal states, echoing previous findings that most noteworthy
tropical cyclone-related tornadoes occur on the right-side of the tropical
cyclone track in Atlantic-basin \ac{US} storms~\parencite{moore2012}.  These
exposure averages are somewhat limited as estimates of long-term frequencies,
as tropical cyclones follow decadal patterns~\parencite{kossin2007more} likely
not adequately captured in the available data. However, exposure assessments
spanning over a century have found similar patterns for distance- and
wind-based metrics~\textcite{zandbergen2009, kruk2010} [double-check that refs
found similar patterns].

\begin{comment}
However, these frequency maps, together with evidence from
specific tropical cyclones (Figures~\ref{fig:ivanexposure}
and~\ref{fig:jaccard}),  do illustrate the potential for strong differences in
spatial patterns in tropical cyclone exposures, depending on which tropical
cyclone hazards are considered.  A few previous studies have sought to
determine county-level exposure to tropical cyclones over multi-year periods,
including~\textcite{zandbergen2009}, which estimated exposure in \ac{US}
counties to all \ac{US} landfalling Atlantic-basin tropical cyclones
between~1851 and~2003, using both a distance-based metric and a metric that
combined distance and windspeed, and~\textcite{kruk2010}, which explored
exposure to hurricane-related winds in the \ac{US}, including inland areas,
for~1900\,--\,2008.  Our results suggest that such exposure assessments may
perform well in capturing some tropical cyclone hazards (e.g., wind), but
likely miss other potentially dangerous tropical cyclone exposures, especially
for hazards that repeatedly threaten northern or inland counties (e.g., rain,
flooding).
\end{comment}

\subsection*{Agreement between exposure metrics}

We found that there was typically only moderate or low agreement between
county-level exposure classifications for a tropical cyclone when comparing
different exposure metrics. This suggests that the use of one of these metrics
as a proxy for all storm-based hazards in epidemiological research would often
be problematic, introducing exposure misclassification.

\begin{comment}
For example, distance from a tropical cyclone's track is relatively easy to
measure and has been used as an operational metric of exposure to tropical
cyclones in previous large-scale studies (examples include ...). Since distance
itself does not constitute a hazard, distance is meant in these cases as a
surrogate to capture exposure to hazards from the tropical cyclone. However,
here we found that in assessing \ac{US} county-level exposure to tropical
cyclones, distance is, at best, a moderate, and often a very poor, surrogate
for exposure to the specific tropical cyclone hazards of high wind, extreme
rainfall, flooding, and tornadoes (Figure~\ref{fig:jaccard}). Therefore, use of
distance to assess tropical cyclone exposure for impact studies could result in
problematic exposure misclassification, which could mask true associations,
even strong associations, between tropical cyclone exposure and outcomes of
interest in impact studies~\parencite{savitz2016interpreting,
armstrong1998effect}.  
\end{comment}

These findings align with previous results from atmospheric science and related
fields on the characteristics of tropical cyclones. While tropical cyclone
rainfall and windspeed are often well-correlated when the tropical cyclone is
over water~\parencite{cerveny2000}, this relationship often does not remain as
strong once the hurricane has made landfall~\parencite{jiang2008}.  Fast-moving
tropical cyclones bring higher risks of dangerous winds
inland~\parencite{kruk2010}, while slow-moving tropical cyclone are likely to
bring more rain~\parencite{rappaport2000} and cause more damage because of
sustained hazardous conditions~\parencite{rezapour2014}. Further, while the
likelihood and extent of flooding during a tropical cyclone is related to the
tropical cyclone's rainfall, it is also driven by factors like top soil
saturation and the structure of the water basin's drainage
network~\parencite{chen2015, rees2001}.

However, we did find a small set of tropical cyclones for which for which
agreement between metrics were unusually high (e.g., Floyd in~1999, Irene in
2011, Hannah in~2008, Bertha in~1996).  Hurricanes Floyd in~1999 and Irene
in~2011 both made their first \ac{US} landfall in North Carolina at minor
hurricane windspeeds (Category~2 and~1, respectively) and then skimmed the
eastern coast of the \ac{US} north through New England, bringing large rainfall
to much of the eastern coast from North Carolina north and causing extensive
inland flooding in North Carolina (Floyd) and New England
(Irene)~\parencite{avila2013atlantic, lawrence2000atlantic}.  Hurricanes Hannah
in~2008 and Bertha in~1996 followed the eastern coastline north of North
Carolina in a pattern similar to Floyd and Irene. For this set of storms, the
tropical cyclones' persistent proximity to water may have helped maintain wind
speeds in similar patterns to rain and distance exposures, resulting in this
moderate to good agreement among exposure assessments based on different
metrics.

In some cases, exposure misclassification from using one of these exposure
metrics to capture one or more of the other storm hazards may be differential
(i.e., associated with the outcome of interest or with factors associated with
risk of the outcome of interest). For example, tropical cyclone wind exposures
tend to be concentrated in counties near the coast, since most tropical
cyclones rapidly decrease in their sustained windspeed following landfall.
However, tropical cyclone exposures based on distance can extend well inland,
following the tropical cyclone's tracks, but may not adequately capture all
wind-exposed counties near the coast. In this case, if the
etiologically-relevant exposure is high wind but exposure is classified based
on distance, the probability of being misclassified as unexposed would be
higher in coastal counties, while the probability of being misclassified as
exposed would be higher in inland counties. If coastal counties differ from
inland counties in either the outcome of interest or in factors associated with
risk of that outcome, differential exposure misclassification would
exist~\parencite{savitz2016interpreting}. Such differential exposure
misclassification can bias estimates of tropical cyclone effects either towards
the null (estimating a lower or null association compared to the true
association that exists) or away from the null (estimating a larger association
than actually exists)~\parencite{savitz2016interpreting, armstrong1998effect}.

\begin{comment}
The use of a single hazard-based metric (e.g., wind) could cause similar
problems if the impact is driven, at least in part, by a different hazard or by
multiple hazards of the tropical cyclone.
\end{comment}

\subsection*{Case study}

Dissimilarity in exposure to specific hazards of tropical cyclones can result
in differing patterns in estimates of county-level exposure
(Figure~\ref{fig:ivanexposure}), which can lead to substantial differences
in estimates of population physical exposure
(Figure~\ref{fig:topelecdependexposure}), based on which storm hazard is
considered. The measure of a hurricane's intensity, the Saffir-Simpson scale,
expresses intensity as a function of wind speed, and so fails to capture
potential risks from other hazards of the storm~\parencite{smith2009}, and
previous assessments of physical exposure to tropical cyclones have often
focused on winds or distance from the storm. For example, a global study of
exposure and vulnerability to natural hazards used a combination of windspeed
above a certain threshold and distance from the storm's track to assess
exposure~\parencite{peduzzi2009assessing}. While many storm impacts might be
most strongly linked to wind hazards, there is a growing recognition of the
potential risks of adverse health outcomes and property damage from rain- and
flood-related tropical cyclone hazards in the \ac{US}~\parencite{smith2009}.
Such assessments may underemphasize potentially dangerous exposures to certain
regions of the \ac{US}, particularly inland locations. In fact, based on our
assessment of physical exposures to tropical cyclones among
electricity-dependent Medicare beneficiaries, the highest expected physical
exposure under any metric was measured for Philadelphia County, PA, under the
flood metric (Figure~\ref{fig:topelecdependexposure}).  While this county has a
similar-sized population of electricity-dependent Medicare beneficiaries as
Miami-Dade County, FL (Figure~\ref{fig:topelecdependexposure}), the frequency
of storm-related flood events in this inland county results in a very high
expected physical exposure among this subpopulation, while this county is not
included in the top ten counties for physical exposure based on most of the
other exposure metrics.

### 2019-07-27 writing/ehp_figures.tex
Work on draft throughout

\begin{figure}%[tbhp]
\centering
\includegraphics[width=16cm]{ivanonly}
\caption{Counties classified as exposed to Hurricane Ivan (2004) under each
exposure metric (Table 1). The red line shows the track of Hurricane Ivan 
based on the revised Atlantic hurricane database (HURDAT2 \cite{landsea2013}).
Similar maps for other large-extent storms are given in Fig. S3.}
\label{fig:ivanexposure} 
\end{figure}

@@

\begin{figure}%[tbhp] 
\centering 
\includegraphics[width = 0.6\linewidth]{jaccard_heatmap} 
\caption{Heatmap of Jaccard index values for
specific exposure metric pairs within storms. Only storms between 1996 and 2011,
and for which at least 250 counties were exposed based on at least one metric,
are included. The color of each cell within the main heatmap indicates the value
of the Jaccard index (proportion of counties classified as exposed by both
metrics out of storms classified as exposed by either metric) for a given pair
of metrics for a given storm. Storms are displayed within clusters that have
similar patterns in county-level exposure agreement for metric pairs, based on
hierarchical clustering using the complete link method
\cite{murtagh2012algorithms} (i.e., storms in the same cluster tend to have
similar patterns for the pairwise strength of agreement among metrics); columns
are also ordered based on hierarchical clustering. The colors to the right of
the main heatmap for each storm indicate the total number of counties classified
as exposed to the storm by any of the five metrics, providing an estimate of
storm extent. Maps are available showing the counties identified as exposed
under each of five metrics for the widest-extent storm in each cluster:
Hurricane Ivan (2004) (Fig. \ref{fig:ivanexposure}) and Hurricanes Floyd (1999),
Lee (2011), Cindy (2005), and Katrina (2005) (Fig. S3).} 
\label{fig:jaccard}
\end{figure}

@@

\begin{figure}%[tbhp] 
\centering
\includegraphics[width=15cm]{averageexposureonly} 
\caption{Average number of storm exposures per decade in U.S. counties for 
each exposure metric. The criteria behind each of the five metrics is given 
in Table \ref{tab:exposuremetrics}. The years used to estimate these averages 
are based on years of available exposure data (distance and wind: 1988--2015; 
rain: 1988--2011; flood and tornado: 1996--2015). Similar patterns persist when
analysis is restricted to years with all exposure data available (1996--2011;
Fig. S5).} 
\label{fig:averageexposure} 
\end{figure}

>>>>

\begin{figure}[tbhp!] \centering
\includegraphics[width=0.7\linewidth]{hurrtracks}
\caption{States and storms considered in this study. All counties in the states
        shown in this map were investigated. The lines show the paths
	of the study storms, which included all tracked storms in 1988\,--\,2015
	\ac{HURDAT2}~\parencite{landsea2013} that came within 250~\si{\kilo\metre} 
	of at least one \ac{US} county. Thicker lines show the tracks 
	of storms whose names have been retired, indicating that the storm was particularly 
	severe or had notable impacts~\parencite{retirednames}.
	}
\label{fig:hurrtracks}
\end{figure}

@@

\begin{figure}[tbhp!] \centering
\includegraphics[width=0.9\linewidth]{raincomparison} 
	\caption{Comparison of storm-associated rainfall estimates between 
	a re-analysis dataset (included as the rainfall exposure metric
	in the open-source data and included in further analysis) and ground-based
	observations in nine sample counties. The rainfall estimates  
	include rainfall from two days before to one day after the storm's closest
	approach to the county. Each small graph shows data for one sample county, 
	and each point shows one tropical storm. The number of storms 
	within each county and the average number of stations reporting rainfall during 
	the county's storms are given above each plot. Horizontal and vertical lines 
	in each plot show the threshold of 75~\si{\milli\metre} used to classify a storm 
	as ``exposed'' in further analysis (Table 1). Note that 
	x- and y-axis ranges differ by county.
	} 
\label{fig:raincomparison}
\end{figure}

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.6\linewidth]{windcomparison}
\caption{Comparison of modeled maximum sustained surface wind speeds 
	(included as the primary wind exposure metric in the open-source
	data and used in further analysis) with estimates from the \ac{HURDAT2}
	wind speed radii. Each point represents a storm, with the x-axis
	giving the percent of counties classified in the same category
	of maximum sustained surface wind speeds ($<$34~\si{\knot}; 
	34\,--\,49.9~\si{\knot}; 50\,--\,63.9~\si{\knot}; 
	$\ge$64~\si{\knot}) by both sets of wind data for that storm. The 
	color of each point indicates the extent of the storm, 
	giving the number of study counties that were exposed to 
	maximum sustained surface wind speeds of at least 34~\si{\knot}
	(based on modeled wind speeds). Estimates are shown for [all?]
	study storms since 2004, the earliest year for which 
	wind speed radii estimates are available in \ac{HURDAT2} [?].
	}
\label{fig:windcomparison}
\end{figure}

\begin{figure}[tbhp!]
\centering
\includegraphics[width=0.8\linewidth]{floodcomparison}
\caption{Comparison for a sample of study counties of NOAA Storm Events
listings versus five-day total streamflows at county streamflow gages during
tropical storms. The number of streamflow gages used in analysis are given in
parentheses beside the county's name in the panel title. Each point represents
a single tropical storm. Note that the x-axis scales differ by county,
depending on the number of streamflow gages and typical flow rates for each
gage, and are on a log-10 scale.}
\label{fig:floodcomparison}
\end{figure}

@@

\begin{figure}%[tbhp] 
\centering
\includegraphics[width=15cm]{averageexposureonly.pdf} 
\caption{Average number of storm exposures per decade in U.S. counties for each
exposure metric. The criteria behind each of the five metrics is given in Table
\ref{tab:exposuremetrics}. The years used to estimate these averages are based
on years of available exposure data (distance and wind:~1988\,--\,2015; rain:
1988\,--\,2011; flood and tornado:~1996\,--\,2015). } 
\label{fig:averageexposure} 
\end{figure}

\begin{figure}%[tbhp]
\centering
\includegraphics[width=16cm]{ivanonly.pdf}
\caption{Counties classified as exposed to Hurricane Ivan in 2004 under each
exposure metric considered (Table~\ref{tab:exposuremetrics}). The red line
shows the track of Hurricane Ivan based on the revised Atlantic hurricane
database \ac{HURDAT2}~\parencite{landsea2013}.  Similar maps for other
large-extent storms are given in Figure~S3.}
\label{fig:ivanexposure} 
\end{figure}

\begin{figure}%[tbhp] 
\centering 
\includegraphics[width = 0.6\linewidth]{jaccard_heatmap.pdf} 
\caption{Agreement between exposure classifications based on different
         exposure metrics for all storms between~1996 and~2011 for which 
	 at least~250 counties were exposed based on at least one metric.
	 Each row shows one storm, and the color of each cell shows the 
	 measured Jaccard index for each pair of exposure metrics 
	 (proportion of counties classified as exposed by both metrics out 
	 of storms classified as exposed by either metric). The colors to the 
	 right of the main heatmap for each storm indicate the total number of 
	 counties classified as exposed to the storm by any of the five metrics, 
	 providing an indication of each storm's extent. Storms are displayed 
	 within clusters that have similar patterns in county-level exposure 
	 agreement for metric pairs, based on hierarchical clustering using the 
	 complete link method~\parencite{murtagh2012algorithms}; columns are also 
	 ordered based on hierarchical clustering. Maps are available showing the 
	 counties identified as exposed under each of five metrics for the widest-extent 
	 storm in each cluster: Hurricane Ivan in~2004 (Figure~\ref{fig:ivanexposure}) 
	 and Hurricanes Floyd in~1999, Lee in~2011, Cindy in~2005, and Katrina 
	 in~2005 (Figure~S3).
} 
\label{fig:jaccard}
\end{figure}

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=15.5cm]{topelecdependexposure}
\caption{Counties with the highest estimated physical exposure among
electricity-dependent Medicare beneficiaries exposed to storms per year in U.S.
counties for each exposure metric. The color of each bar indicates the number
of Medicare beneficiaries in the county reliant on electricity-dependent
medical and assistive equipment as of July~2017. The length
of each bar shows the average expected number of these electricity-dependent
Medicare beneficiaries exposed to tropical storms per year based on a given
exposure metric.}
\label{fig:topelecdependexposure}
\end{figure*}
